Missing The Point

### 2020-09-22 Manuscript.Rmd
New regression coefficient, 100 sims

## Check if heuristic for AC works
```{r}
load("~/MissingThePoint/Data/convergence_diagnostics_test.Rdata")
convergence_diagnostics %>% filter(sim == 1, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.qhat)) + geom_line()
convergence_diagnostics %>% filter(sim == 1, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.lambda)) + geom_line()
```

>>>>

## Check if heuristic for AC works
```{r}
# load("~/MissingThePoint/Data/diagnostics.Rdata")
# load("~/MissingThePoint/Data/raw_outcomes.Rdata")
sim_nr <- 3
outcomes[[sim_nr]] %>% filter(mech == "MCAR", p == 0.95) %>% ggplot(aes(x=it, y = est)) + geom_line()
convergence_diagnostics %>% filter(sim == sim_nr, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.qhat)) + geom_line()
convergence_diagnostics %>% filter(sim == sim_nr, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.lambda)) + geom_line()
```

## Example data

```{r}
# environment
library(mice)
set.seed(123)

# functions
source("~/MissingeThePoint/R/ComputeDiagnostics.R")

not_all_na <- function(x) {
  !all(is.na(x))
}

preprocess_thetas <- function(theta, ext){
  out <- theta %>% 
  as.data.frame() %>% 
  t() %>% 
  as.data.frame() %>%
        setNames(paste0(ext, ".", names(.))) %>%
        cbind(
          it = 1:n_it,
          m = rep(1:n_imp, each = n_it),
          .
        ) %>% 
    select_if(not_all_na) %>% 
    arrange(it)
  rownames(out) <- NULL
  return(out)
}

get_diagnostics <- function(parameters) {
  thetas <- names(parameters)[-c(1:2)]
  out <- purrr::map_dfc(thetas, function(tt) {
    matrix(parameters[[tt]], ncol = n_imp, byrow = T) %>%
      convergence() %>%
      select(r.hat.max, ac.max) %>%
      setNames(., paste0(names(.), ".", tt))
  }) %>%
    cbind(it = 1:n_it, .)
  return(out)
}

impute_once <- function(iteration, ...) {
  if(is.null(mids)){
    mids <<- mice(boys, m = n_imp, maxit = 1, printFlag = FALSE)
  }
  else {
    mids <<- mice.mids(mids, printFlag = FALSE)
  }
  mira <- mids %>% mice::lm.mids(age ~ ., data = .) 
  mipo <- mira %>%
    mice::pool() %>%
    summary(., conf.int = TRUE)
  out <- data.frame(it = iteration, est = mipo[["estimate"]][2])
  return(out)
}

# parameters
n_imp <- 5
n_it <- 10

# analyses
mids <- NULL
ests <- purrr::map_dfr(1:n_it, function(it){impute_once(iteration = it)})
param <- preprocess_thetas(mids$chainMean, ext = "mu") %>% 
  dplyr::full_join(
      preprocess_thetas(mids$chainVar, ext = "sigma")
  )
convs <- get_diagnostics(param)
res <- full_join(ests, convs)
# plot
ggplot(conv, aes(x = it, y = ac.max.mu.hgt)) +
  geom_line()

# more analyses
imp2 <- mice(boys, m = n_imp, maxit = 1, printFlag = FALSE, seed = 123)
mice.mids(imp2)
```
